---
title: "STA6235 Week 12"
author: "Your Name Here"
format: 
  html:
    self-contained: true
execute:
  echo: true
  warning: false
  message: false
  error: true
editor: source
---

For all questions below, please return to the labs for the stated weeks and copy over necessary code to (1) pull in the dataset, (2) construct the models.

## Linear Regression - Week 4

**1. Construct the following models:**

- **M1: Model penguin body mass (*body_mass_g*) as a function of species (*species*), flipper length (*flipper_length_mm*), bill length (*bill_length_mm*), and the interaction between flipper length and bill length.**

- **M2: Model penguin body mass (*body_mass_g*) as a function of species (*species*), flipper length (*flipper_length_mm*), and bill length (*bill_length_mm*).**

**Perform 5-fold cross-validation to determine which model fits better. Remember to draw your conclusion and state why you drew that conclusion.**

```{r}

```

## Gamma Regression - Week 5

**2. Construct the following models:**

- **M1: Model HbA1c (*HbA1c*) as a function of age (*age*), waist circumference (cm; *waist*), hypertension medication use (*BPmeds*; 1 = takes blood pressure lowering medication, 0 = does not take blood pressure lowering drugs), and the interaction between age and hypertension medication use.**

- **M2: Model HbA1c (*HbA1c*) as a function of age (*age*), waist circumference (cm; *waist*), and hypertension medication use (*BPmeds*; 1 = takes blood pressure lowering medication, 0 = does not take blood pressure lowering drugs).**

**Perform leave-one-out cross-validation to determine which model fits better. Remember to draw your conclusion and state why you drew that conclusion.**

```{r}

```

## Logistic Regression - Week 7

**3. Construct the following models:**

- **M1: Model if the culprit was caught by either Scooby or Shaggy (the variable you created in Q2) as a function of the number of times either "zoinks!" or "jeepers!" was said on the show (the variable you created in Q3), if Scrappy Doo was in the episode (*scrappy_doo*), and the number of snacks eaten during the episode (*number_of_snacks*).**

- **M2: Model if the culprit was caught by either Scooby or Shaggy (the variable you created in Q2) as a function of the number of times either "zoinks!" or "jeepers!" was said on the show (the variable you created in Q3).**

**Perform 10-fold cross-validation to determine which model fits better. Remember to draw your conclusion and state why you drew that conclusion.**

```{r}

```

## Poisson and Negative Binomial Regressions - Week 10

**4. Construct the following models using the negative binomial distribution:**

- **M1: Model the number of candidate votes (*candidatevotes*) as a function of year (*year*), party (*party*), region (*region*), and the interaction between party and year.**

- **M2: Model the number of candidate votes (*candidatevotes*) as a function of year (*year*), party (*party*), and region (*region*).**

**Perform leave-one-out cross-validation to determine which model fits better. Remember to draw your conclusion and state why you drew that conclusion.**
